CODECHECK: An open-science initiative for the independent execution of computations underlying research articles

### 2021-01-12 codecheck-paper.tex
restructure related work and resolve open issues

The journal \emph{ACM Transactions on Mathematical Software (TOMS)} 
established a "Replicated Computational Results" (RCR) review process
\cite{heroux_editorial_2015} (using "replicable" with the same meaning 
as CODECHECK uses "reproducible").
The CODECHECK principles were independently developed as we only later 
learned about TOMS RCR, which we judge as fulfilling CODECHECK principles
1 to 4.
Our CODECHECK provides more extensive discussion of the possible variants, 
while TOMS RCR realises one particular workflow for reproducibility 
reviews for one particular journal. \cite{heroux_editorial_2015}
include similar concerns about
selection of reviewers as above. Unlike existing CODECHECK certificates, 
the RCR reports undergo editorial review, but this could very well become
part of CODECHECK workflows at journals.
The publication of the RCR report is seen as a reward for the efforts of
the reproducing person, while the possible conflict of interest of this 
motivation is acknowledged. TOMS also recognises reviewer activity in a 
partnership with Publons
\footnote{\url{https://authors.acm.org/author-services/publons}},
though it is unclear if the author of an RCR report receives both the report
authorship and the reviewer recognition. In any case, this is different
from CODECHECK, which specifically aims at recognition as reviewers.
In our view, this removes the possible conflict of interest while keeping
the public acknowledgement.

Specific to the field of Mathematics, the RCR was also  expected to apply a
review of the software itself if the system it runs on cannot be evaluated by
an independent party.
The TOMS RCR also notes the importance of communication and expects
collaboration between author and RCR reviewers.
The TOMS creators share thoughts around reviewer selection and also put trust
in reviewer judgement over numerical bit-wise perfection.
A key difference is that authors opt-in with an \emph{RCR Review Request} and
the RCR reports, which are very similar to CODECHECK certificates, are
published in the TOMS journal next to the actual papers.
A search on Crossref\footnote{\url{https://search.crossref.org/?q=\%22Replicated+Computations+Results+\%28RCR\%29+Report\%22&from_ui=yes&page=2}; search executed
on 2020-12-10} shows 15 RCR Reports to be published and the workflow to be 
extended to the ACM journal \emph{Transactions on Modeling and Computer 
  Simulation (TOMACS)}
%% SJE TODO - fix footnote
%% \footnote{\url{https://dl.acm.org/journal/tomacs/author-guidelines-%35-rcrini}}.

% 8: https://scholar.google.de/scholar?start=10&q=Replicated+Computations+Results+%22(RCR)+Report%22&hl=de&as_sdt=0,5
% 15: https://search.crossref.org/?q=Replicated+Computations+Results+%22%28RCR%29+Report%22&from_ui=yes&publication=ACM+Transactions+on+Mathematical+Software
% 15: https://academic.microsoft.com/search?q=Replicated%20Computations%20Results%20%22(RCR)%20Report%22&f=&orderBy=0&skip=10&take=10

A number of journals or conferences/workshops provide guidelines for ensuring reproducible publications and their verification.
These include, for example, \ldots{}
% first glimpse into "Code exeuction processes in scholarly publishing" ?
% `https://docs.google.com/document/d/1fMWrFvBTwAYXg5J_bYIjgb-gY7DfQ0DOjx9Vlg_Rbmg/edit# ?
\emph{Information Systems}, with an invited reproducibility paper track
\footnote{\url{https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors}}

Another journal initiative is more indirectly connected with reproductions.
\emph{Nature Machine Intelligence} recently introduced a new type of article,
the reusability report \cite{noauthor_research_2020}.
Inspired by the detailed and nuanced submissions to a reproducibility 
challenge, the reusability report focuses on the exploration of robustness
and generalizability of the original paper's claims
\cite{noauthor_research_2020}. This answers the specific community's 
challenges around computational reproducibility and also values these kind
of contributions as independent publications, which goes beyond the goals 
of CODECHECK.

However, no approach besides CODECHECK spans across journals and is
intentionally designed to be picked up and implemented by many different 
journals or events, and to build a community of codecheckers. CODECHECK shares
this interdisciplinary nature with other community initiatives concerned with 
reproducibility awareness, education, and supports, such as ReproHack
\footnote{\url{https://reprohack.github.io/reprohack-hq/}}, Code Copilot
\footnote{\url{https://twitter.com/Code_Copilot}}, or Papers with Code
\footnote{\url{https://paperswithcode.com/about}}.
The latter recently announced a collaborations with the preprint server
\emph{arXiv} on providing data and code supplements for machine learning
manuscripts\footnote{\url{https://medium.com/paperswithcode/papers-with-code-partners-with-arxiv-ecc362883167}} and runs a reproduciblity challenge
\footnote{\url{https://paperswithcode.com/rc2020}}.
% Papers with Code now also does more disciplines than just ML.
Likewise, different disciplines and journals provide reproducibility
checklists, e.g., \cite{rosenberg_next_2020}, which naturally share some
aspects while addressing particularities as well as addressing researchers
from different fields. Regarding the education and guidance for authors, 
we see CODECHECK's role in referencing and linking educational efforts
and helpful material, not as a creator and maintainer of content.

The journal \emph{ReScience C} publishes replications
\footnote{\url{https://rescience.github.io/faq/}};
they do not accept proprietary software and require open source code;
they also required a third party to replicate; they also use Zenodo
to issue DOIs.
The journal \emph{Cortex} has a special article type 
\emph{Verification Reports}, which  actually are about replication of results 
but are very well designed/reasoned \cite{chambers_verification_2020}.
In a similar vein, the CODECHECK certificates
could also be published as a special article type within journals.

For research with very high stakes, where reproduction would be too weak and
post publication replication possibly too late because of policy impact,
\cite{benjamin-chung_internal_2020} propose \emph{internal replication}.
A workflow that underwent internal
replication would very likely be of high quality and relatively easy to codecheck.
In a similar vein, internal codechecks may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission. The guidelines
for CODECHECK can be used by fellow/not independent lab members just as well.

Gavis and Donoho \cite{gavish_universal_2011} propose a new discipline and 
infrastructure for reproducible computational research with its own tools and
API. Their specific packaging format, provenance record, and cryptographic
\emph{Verifiable Result Identifier} would indeed provide excellent
reproduciblity. However, the system is also complex and was not taken up by
any publisher as far as we know; the system is indeed not open source itself.
In comparison, CODECHECK is less powerful but also much more flexible and
less dependent on specific tools or infrastructure. If data and code are 
deposited properly, i.e., very unlike to disappear, then the certificate's 
DOI is practically quite close to the cryptographic identifier.

Local reproduction initiatives/services:
\href{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/}{CISER R-squared}
(established/permanent),
\href{https://go.wwu.de/r2s2}{WWU R2S2} (pilot only, focused on reproductions),
\href{https://github.com/OxfordCodeReviewNet/forum}{Oxford code review network (OxCRN)}
(community, broader scope), \href{https://isps.yale.edu/research/data/approach}{YARD 
at Yale} with dedicated staff for replications.
For these, the CODECHECK scope, tools, and practical experiences may be
helpful resources.

@@

>>>>

The journal \emph{ACM Transactions on Mathematical Software (TOMS)} 
established a "Replicated Computational Results" (RCR) review process
\cite{heroux_editorial_2015} (using "replicable" with the same meaning 
as CODECHECK uses "reproducible").
A search on Crossref\footnote{\url{https://search.crossref.org/?q=\%22Replicated+Computations+Results+\%28RCR\%29+Report\%22&from_ui=yes&page=2}; search executed
on 2020-12-10.} shows 15 RCR Reports to be published and the 
% Number of found TOMAS RCR reports:
% 8: https://scholar.google.de/scholar?start=10&q=Replicated+Computations+Results+%22(RCR)+Report%22&hl=de&as_sdt=0,5
% 15: https://search.crossref.org/?q=Replicated+Computations+Results+%22%28RCR%29+Report%22&from_ui=yes&publication=ACM+Transactions+on+Mathematical+Software
% 15: https://academic.microsoft.com/search?q=Replicated%20Computations%20Results%20%22(RCR)%20Report%22&f=&orderBy=0&skip=10&take=10
workflow to be 
extended to the ACM journal \emph{Transactions on Modeling and Computer 
Simulation (TOMACS)}\footnote{\url{https://dl.acm.org/journal/tomacs/author-guidelines}}.

The CODECHECK principles were independently developed as we only later 
learned about TOMS RCR, which we judge as fulfilling CODECHECK principles
1 to 4.
This work provides an extensive discussion of the possible variants, 
while TOMS RCR realises one particular workflow for reproducibility 
reviews for one particular journal. The TOMS editorial
\cite{heroux_editorial_2015} shares similar concerns about
selection of reviewers as above. Unlike existing CODECHECK certificates, 
the RCR reports undergo editorial review, but this could very well become
part of CODECHECK processes at journals.
The publication of the RCR report is seen as a reward for the efforts of
the reproducing person, while the possible conflict of interest of this 
motivation is acknowledged. TOMS also recognises reviewer activity in a 
partnership with Publons\footnote{
\url{https://authors.acm.org/author-services/publons}},
though it is unclear if the author of an RCR report receives both the report's
authorship and the reviewer recognition. In any case, this is different
from CODECHECK, which specifically aims at recognition as reviewers.
In our view, the reviewer role removes the possible conflict of interest while
keeping the public acknowledgement.
Specific to the field of Mathematics, the RCR is also expected to apply a
review of the software itself if the system it runs on cannot be evaluated by
an independent party.
The TOMS RCR creators concur with the importance of communication, expect
collaboration between author and RCR reviewers,
share the considerations around reviewer selection, and also put trust
in reviewer judgement over numerical bit-wise perfection.
A key difference is that authors opt-in with an \emph{RCR Review Request} and
the RCR reports, which are very similar to CODECHECK certificates, are
published in the TOMS journal next to the actual papers.

A number of journals provide guidelines for 
ensuring reproducible publications and their verification,
e.g.,~\emph{Information Systems} with its invited 
reproducibility paper track\footnote{
\url{https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors}.}.
% first glimpse into "Code exeuction processes in scholarly publishing" ?
% `https://docs.google.com/document/d/1fMWrFvBTwAYXg5J_bYIjgb-gY7DfQ0DOjx9Vlg_Rbmg/edit# ?
\emph{Nature Machine Intelligence} recently introduced a new type of article,
the reusability report \cite{noauthor_research_2020}.
Inspired by the detailed and nuanced submissions to a reproducibility 
challenge, the reusability report focuses on the exploration of robustness
and generalizability of the original paper's claims
\cite{noauthor_research_2020}. This answers the specific community's 
challenges around computational reproducibility and also values these kind
of contributions as independent publications, which goes beyond the goals 
of CODECHECK.
The journal \emph{Cortex} has a special article type 
\emph{Verification Reports}, which  actually are about replication of results 
but are very well designed/reasoned \cite{chambers_verification_2020}.
In a similar vein, the CODECHECK certificates
could also be published as a special article type within journals.

Going beyond article types, the journal \emph{ReScience C} publishes only
replications\footnote{\url{https://rescience.github.io/faq/}} requiring
open code and replication by a third party to. ReScience also relies on
free infrastructure (GitHub and Zenodo).
For research with very high stakes, where reproduction would be too weak and
post publication replication possibly too late because of policy impact,
Benjamin-Chung et~al. \cite{benjamin-chung_internal_2020} propose
\emph{internal replication}.
A workflow that underwent internal
replication would very likely be of high quality and relatively easy to check.
Similarly, internal CODECHECKs may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission.
Such internal checks are professionalised in local reproduction services,
such as CISER R-squared\footnote{
\url{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/}},
} (established/permanent),
%Uni Münster's Reproducible Research Support Service\footnote{
%\url{https://go.wwu.de/r2s2}} (pilot),
Oxford's code review network (OxCRN)\footnote{
\url{https://github.com/OxfordCodeReviewNet/forum}} (community, broader scope), or
Yale's YARD\footnote{
\url{https://isps.yale.edu/research/data/approach}} (staff for replications).

Gavis and Donoho \cite{gavish_universal_2011} propose a new discipline and 
infrastructure for reproducible computational research with its own tools and
API. Their specific packaging format, provenance record, and cryptographic
\emph{Verifiable Result Identifier} would indeed provide excellent
reproduciblity. However, the system is also complex and was not taken up by
any publisher as far as we know; the system is indeed not open source itself.
In comparison, CODECHECK is less powerful but also much more flexible and
less dependent on specific tools or infrastructure. If data and code are 
deposited properly, i.e.,~very unlikely to disappear, then the certificate's 
DOI is practically close to the cryptographic identifier.

@@

No approach besides CODECHECK spans across journals and is
intentionally designed to be picked up and implemented by many different 
journals or events, and to build a community of codecheckers. CODECHECK shares
its interdisciplinary nature with other community initiatives concerned with 
reproducibility awareness, education, and supports, such as ReproHack
\footnote{\url{https://reprohack.github.io/reprohack-hq/}}, Code Copilot
\footnote{\url{https://twitter.com/Code_Copilot}}, or Papers with Code
\footnote{\url{https://paperswithcode.com/about}}.
The latter recently announced a collaborations with the preprint server
\emph{arXiv} on providing data and code supplements for machine learning
manuscripts\footnote{\url{https://medium.com/paperswithcode/papers-with-code-partners-with-arxiv-ecc362883167}} and runs a reproduciblity challenge
\footnote{\url{https://paperswithcode.com/rc2020}}.
% Papers with Code now also does more disciplines than just ML.
Likewise, different disciplines and journals provide reproducibility
checklists, e.g.,~\cite{rosenberg_next_2020}, which naturally share some
aspects while addressing particularities as well as addressing researchers
from different fields. Regarding the education and guidance for authors, 
we see CODECHECK's role in referencing and linking educational efforts
and helpful material, not as a creator and maintainer of such content.
